Theories of deliberated choice

### 2024-05-06 simple.tex
Second attempt about claims about (strict) types also seems to fail

\begin{conjecture}
  Consider a mapping ${\allleadstog} \in (P^{\allhists})^I$. Define $E$ as the equivalence classes in $I$ that considers as equivalent all $i$ mapped to the same element of $P^{\allhists}$.
  A wide-shuffling over $I$ is a mapping $\sigma_{\allleadstog} \in I^I$ that reaches any equivalence class in $E$, thus $\forall e \in E: \exists i \suchthat \sigma_{\allleadstog}(i) \in e$.
  The bijections over $I^I$ are a subset of the wide-shufflings (those that also are bijections per $e \in E$, thus $\forall e \in E: \restr{\sigma_{\allleadstog}}{e}$ bijects with its image).

  A claim $C$ is not about types iff $\exists {\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling, such that $({\allleadstog} \circ \sigma_{\allleadstog}) \notin C$.
\end{conjecture}
\begin{proof}
  % Consider that $\exists {\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling, such that $({\allleadstog} \circ \sigma_{\allleadstog}) \notin C$.
  Consider a claim $C$ about types $S$.
  Consider any ${\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling.
  As ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$.
  Also, ${\allleadstog}(\sigma_{\allleadstog}(I)) = {\allleadstog}(I)$. 
  Thus, ${\allleadstog}(\sigma_{\allleadstog}(I)) \wsub S$.
  Thus, $({\allleadstog} \circ \sigma_{\allleadstog}) \in C$.

  About the converse, given $C$, 
  define $S = \bigcup_{{\allleadstog} \in C}({\allleadstog}(I))$,
  and assuming that 
  $[\forall {\allleadstog} \in C, \sigma_{\allleadstog}: ({\allleadstog} \circ \sigma_{\allleadstog}) \in C]$, let us show that 
  $C = S^I$, equivalently, that $C = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
  First, considering any ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$ by definition of $S$.
  Second, considering any ${\allleadstog} \notin C$, 
\end{proof}
\begin{conjecture}
  Consider a claim that is not about types but is anonymous. What’s that?
  Example: the claim “everyone has the same behavior”.

>>>>

\begin{conjecture}
  Consider a mapping ${\allleadstog} \in (P^{\allhists})^I$. 
  Define $E$ as the equivalence classes in $I$ that considers as equivalent all $i$ mapped to the same element of $P^{\allhists}$.
  Recall that the bijections over $I$ are the subset of $I^I$ that are bijections per $e \in E$, thus $s \in I^I$ is a bijection over $I$ iff $\forall e \in E: \restr{s}{e}$ bijects with its image.

  A claim $C$ is not about types iff $\exists {\allleadstog} \in C, s \in I^I \suchthat ({\allleadstog} \circ s) \notin C$.
\end{conjecture}
\begin{proof}
  Consider a claim $C$ about types $S$,
  thus,
  $C = S^I = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
  Consider any ${\allleadstog} \in C$ and $s \in I^I$.
  As ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$.
  Also, ${\allleadstog}(s(I)) \wsub {\allleadstog}(I)$. 
  Thus, ${\allleadstog}(s(I)) \wsub S$.
  Thus, $({\allleadstog} \circ s) \in C$.

  About the converse, given $C$, 
  define $S = \bigcup_{{\allleadstog} \in C}({\allleadstog}(I))$,
  and assuming that 
  $[\forall {\allleadstog} \in C, s: ({\allleadstog} \circ s) \in C]$, let us show that 
  $C = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
  First, considering any ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$ by definition of $S$.
  Second, considering any ${\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \in S$,

\end{proof}
\begin{conjecture}
  Consider a claim that is not about types but is anonymous. What’s that?
  Example: the claim “everyone has the same behavior”.
